---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# polyesterData

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/polyesterData)](https://CRAN.R-project.org/package=polyesterData)
<!-- badges: end -->

polyesterData is a package that loads a simulated OMOP CDM dataset of approximately 6039 patients originally sourced from Synthetic Health's Synthea using the [polyester2 R package](https://meerapatelmd.github.io/polyester2/). The csvs can also be direcly accessed in the `data-raw` subdirectory for non-R users.  
  
  
## Installation

You can install the latest version of polyesterData with:

``` r
devtools("meerapatelmd/polyesterData")
```
  
  
## Load Data  

Loading the Drug Exposure Table as an example:  

```{r example}
library(polyesterData)  
```


```{r}
head(DRUG_EXPOSURE)
```



## Statistics  

```{r statistics, echo=FALSE,eval=TRUE}
tables <- c('ALL_VISITS', 'ASSIGN_ALL_VISIT_IDS', 'ATTRIBUTE_DEFINITION', 'CARE_SITE', 'CDM_SOURCE', 'COHORT_DEFINITION', 'CONDITION_ERA', 'CONDITION_OCCURRENCE', 'COST', 'DEVICE_EXPOSURE', 'DOMAIN', 'DOSE_ERA', 'DRUG_ERA', 'DRUG_EXPOSURE', 'FACT_RELATIONSHIP', 'FINAL_VISIT_IDS', 'LOCATION', 'LOCATION_HISTORY', 'MEASUREMENT', 'METADATA', 'NOTE', 'NOTE_NLP', 'OBSERVATION', 'OBSERVATION_PERIOD', 'PAYER_PLAN_PERIOD', 'PERSON', 'PROCEDURE_OCCURRENCE', 'PROVIDER')


output <- list()
for (table in tables) {
        output[[length(output)+1]] <-
                rubix::summarize_variables(get(table), incl_num_calc = FALSE) %>%
                dplyr::select(-DISTINCT_VALUES)
}
names(output) <- tables
output <-
        output %>%
        dplyr::bind_rows(.id = "Table") %>%
        dplyr::select(Table, Variable, COUNT, DISTINCT_COUNT)
options(tibble.print_max = Inf)
options(tibble.width = Inf)
print(output, 200)
```

  
## Code of Conduct

Please note that the polyesterData project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.  

